Isabelle/C/Clean - A Show-Case for a Semantic Back-End for Isabelle/C

### 2019-10-30 C11-BackEnds/Clean_wrapper/document/root.tex
improved the doc structure
build
clean
permute some paragraphs
document
synchronize root.bib

\newenvironment{matharray}[1]{\[\begin{array}{#1}}{\end{array}\]} % from 'iman.sty'
\newcommand{\indexdef}[3]%
{\ifthenelse{\equal{}{#1}}{\index{#3 (#2)|bold}}{\index{#3 (#1\ #2)|bold}}} % from 'isar.sty'
\newcommand{\isactrlC}{{\isacommand C}}
\newcommand{\isactrlMLPRIME}{{\isacommand MLPRIME}}

@@

\begin{abstract}
Isabelle/C~\cite{TuongWolff19} is a C front-end for Isabelle/PIDE providing
generic support for C parsing, editing, and highlighting. Isabelle/C also
provides a generic interface for semantic interpretations of C11 programs and
program fragments. In particular, Isabelle/C also offers the generic framework
to define \emph{annotation commands} and \emph{C antiquotations} that can be
custumized to a specific semantic back-end.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \input{session}
\newpage
\inputif{1/document/Init.tex}
%\inputif{1/document/Meta_C.tex}
\inputif{1/document/Core.tex}
%\inputif{1/document/Isabelle_code_runtime.tex}
%\inputif{1/document/Isabelle_typedecl.tex}
%\inputif{1/document/Generator_dynamic_sequential.tex}
\inputif{1/document/Backend.tex}

%\inputif{2/document/IsPrime_sqrt_outside.tex}
%\inputif{2/document/Clean_backend_old.tex}
\inputif{2/document/Prime.tex}
\inputif{2/document/Quicksort2.tex}
\inputif{2/document/Quicksort.tex}

%\newpage
%\chapter{Appendix}

>>>>

\newenvironment{matharray}[1]{\[\begin{array}{#1}}{\end{array}\]} % from 'iman.sty'
\newcommand{\indexdef}[3]%
{\ifthenelse{\equal{}{#1}}{\index{#3 (#2)|bold}}{\index{#3 (#1\ #2)|bold}}} % from 'isar.sty'
\newcommand{\isactrlC}{{\isacommand C}}
\newcommand{\isactrlmkUNDERSCOREstring}{\isakeywordcontrol{mk{\isacharunderscore}string}}
\newcommand{\isactrlMLPRIME}{{\isacommand ML{\isacharprime}}}

@@

\begin{abstract}
Isabelle/C~\cite{Tuong-IsabelleC:2019} is a C front-end for Isabelle/PIDE
providing generic support for C parsing, editing, and highlighting. Isabelle/C
also provides a generic interface for semantic interpretations of C11 programs
and program fragments. In particular, Isabelle/C also offers the generic
framework to define \emph{annotation commands} and \emph{C antiquotations} that
can be custumized to a specific semantic back-end.

@@

\inputif{1/document/Clean_Wrapper.tex}

\inputif{2/document/Prime.tex}
\inputif{2/document/IsPrime_sqrt_outside.tex}
\inputif{2/document/Quicksort.tex}
\inputif{2/document/Quicksort2.tex}

\inputif{1/document/Init.tex}
\inputif{1/document/Meta_C.tex}
\inputif{1/document/Core.tex}
\chapter{Appendix: Miscellaneous (Interface to ``typedecl'')}
\inputif{1/document/Isabelle_code_runtime.tex}
\chapter{Appendix: Miscellaneous (Overloading ``code\_reflect'')}
\inputif{1/document/Isabelle_typedecl.tex}
\inputif{1/document/Generator_dynamic_sequential.tex}
\inputif{2/document/Clean_backend_old.tex}
